The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-08-13 albatros_paper.tex
HCC added acknowledgment to Raul
HCC added acknowledgments to NSERC and PCSP

We gratefully acknowledge the National Research Foundation (grant
number 110929) and the South African National Antarctic Programme for
providing funding and logistical support for our research program.
The financial assistance of the South African SKA Project (SKA SA)
towards this research is hereby acknowledged (\url{www.ska.ac.za}).
We additionally extend our sincere gratitude to the staff at SKA SA
for hosting our lab tests.  We thank the South African National Space
Agency for their technical support, the crew of Ultimate Heli for
safely delivering us and our cargo, and all of the Marion takeover and
winter team members who provided invaluable advice and field help.
The authors also wish to thank members of the LWA and RAPID
collaborations for useful discussions.

>>>>

We gratefully acknowledge the National Research Foundation (grant
number 110929), the South African National Antarctic Programme, the
Natural Sciences and Engineering Research Council of Canada (grant
number RGPNS-2019-534549), and the Polar Continental Shelf Program for
providing funding and logistical support for our research program.
The financial assistance of the South African SKA Project (SKA SA)
towards this research is hereby acknowledged (\url{www.ska.ac.za}).
We additionally extend our sincere gratitude to the staff at SKA SA
for hosting our lab tests.  We thank the South African National Space
Agency for their technical support, the crew of Ultimate Heli for
safely delivering us and our cargo, and all of the Marion takeover and
winter team members who provided invaluable advice and field help.
The authors also wish to thank members of the LWA and RAPID
collaborations for useful discussions, and Raul Monsalve for helping
make our first MARS campaign a success.
